---
title: "Tsibble"
author: "Kevin O'Brien"
date: "24 September 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tsibble)
```

## build_tsibble Low-level construction of a tsibble object
Description • build_tsibble() creates a tbl_ts object with more controls. It is useful for creating a tbl_ts internallyinsideafunction,anditallowsuserstodetermineifthetimeneedsordering and the interval needs calculating. • build_tsibble_meta() assigns the attributes to an object, assuming this object is a valid tsibble.

#### Usage 
<pre><code>
build_tsibble(x, key, index, index2, groups = id(), regular = TRUE, 
 validate = TRUE, ordered = NULL, interval = NULL)
build_tsibble_meta(x, key, index, index2, groups = id(), regular = TRUE, ordered = NULL, interval = NULL)
</code></pre>

#### Arguments 
* x A data.frame, tbl_df, tbl_ts, or other tabular objects. 
* key Structural variable(s) that deﬁne unique time indices, used with the helper id. If a univariate time series (without an explicit key), simply call id(). See below for details. index A bare (or unquoted) variable to specify the time index variable. index2 A candidate of index to update the index to a new one when index_by. By default, it’s identical to index. 
* groups Grouping variable(s) when group_by.tbl_ts. regular Regular time interval (TRUE) or irregular (FALSE). The interval is determined by the greatest common divisor of positive time distances, if TRUE. 
validate TRUE suggests to verify that each key or each combination of key variables lead touniquetimeindices(i.e. a valid tsibble). Itwillalsomakesurethatthenested variables are arranged from lower level to higher, if nested variables are passed to key. 
 - If you are sure that it’s a valid input, specify FALSE to skip the checks. ordered ThedefaultofNULLarrangesthekeyvariable(s)ﬁrstandthenindexfrompastto future. TRUE suggests to skip the ordering as x in the correct order. 
 - FALSE also skips the ordering but gives a warning instead. 
  -interval NULL computes the interval. Use the speciﬁed interval via new_interval() as is, if an class of interval is supplied.

#### Examples
```{r}
# Prepare `pedestrian` to use a new index `Date` ---
pedestrian %>% build_tsibble( key = key(.), index = !! index(.), index2 = Date, 
interval = interval(.) )
```

## case_na A thin wrapper of dplyr::case_when() if there are NAs

#### Description 
A thin wrapper of ``dplyr::case_when()`` if there are NAs

#### Usage
case_na(formula)

#### Arguments 
* ``formula``: A two-sided formula. The LHS expects a vector containing NA, and the RHS gives the replacement value.

#### Examples
```{r}
x <- rnorm(10) 
x[c(3, 7)] <- NA_real_ 
case_na(x ~ 10) 
case_na(x ~ mean(x, na.rm = TRUE))
```
