## guess_frequency 
Guess a time frequency from other index objects

#### Description 
A possible frequency passed to the ``ts()`` function

#### Usage
<pre><code>
guess_frequency(x)
</code></pre>

#### Arguments 
* x An index object including "yearmonth", "yearquarter", "Date" and others.

#### Details 
If a series of observations are collected more frequently than weekly, it is more likely to have multiple seasonalities. 
This function returns a frequency value at its nearest ceiling time resolution. 

For example, hourly data would have daily, weekly and annual frequencies of 24, 168 and 8766 respectively, and hence 
it gives 24.


#### Examples
```{r}
guess_frequency(yearquarter(seq(2016, 2018, by = 1 / 4))) 
```

```{r}
guess_frequency(yearmonth(seq(2016, 2018, by = 1 / 12))) 
```

```{r}
guess_frequency(seq(as.Date("2017-01-01"), as.Date("2017-01-31"), by = 1)) 
```

```{r}
guess_frequency(seq( as.POSIXct("2017-01-01 00:00"), 
as.POSIXct("2017-01-10 23:00"), by = "1 hour" ))
```
#### References

## key_update Change/update key variables for a given tbl_ts

#### Description
Change/update key variables for a given tbl_ts

#### Usage
key_update(.data, ..., validate = TRUE)

#### Arguments
* .data A tbl_ts. ... Expressions used to construct the key: • unspeciﬁed: drop every single variable from the old key. 
• | and , for nesting and crossing factors. validate TRUE suggests to verify that each key or each combination of key variables lead touniquetimeindices(i.e. avalidtsibble). 

Itwillalsomakesurethatthenested variables are arranged from lower level to higher, if nested variables are passed to key. 
If you are sure that it’s a valid input, specify FALSE to skip the checks.

#### Examples
```{r}
# tourism could be identified by Region and Purpose ---tourism %>% key_update(Region, Purpose)

```

## measured_vars Return measured variables
Description Return measured variables

#### Usage
<pre><code>
measured_vars(x)
</code></pre>
Arguments x A tbl_ts.

#### Examples
measured_vars(pedestrian) measured_vars(tourism)



## pull_interval Extract time interval from a vector

#### Description 
Assuming regularly spaced time, the pull_interval() returns a list of time components as the "interval" class.

#### Usage
pull_interval(x)

#### Arguments 
x AvectorofPOSIXt, Date, yearmonth, yearquarter, difftime, hms, integer, numeric.

#### Details 
``index_valid()`` and ``pull_interval()`` make a tsibble extensible to support custom time index.

Value an "interval" class (a list) includes "year", "quarter", "month", "week", "day", "hour", "minute", "second", "millisecond", "microsecond", "nanosecond", "unit".

#### Examples
```{r}
x <- seq(as.Date("2017-10-01"), as.Date("2017-10-31"), by = 3) pull_interval(x)
```
