---
title: "Tsibble"
author: "Kevin O'Brien"
date: "24 September 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tsibble)
```
## ``units_since`` Time units since Unix Epoch

#### Description 
Time units since Unix Epoch

#### Usage
units_since(x)
Arguments x An object of POSIXct, Date, yearweek, yearmonth, yearquarter.
Details origin: • POSIXct: 1970-01-01 00:00:00 • Date: 1970-01-01 • yearweek: 1970 W01 (i.e. 1969-12-29) • yearmonth: 1970 Jan • yearquarter: 1970 Qtr1

#### Examples
```{r}
units_since(x = yearmonth(2012 + (0:11) / 12))
```

## yearweek Represent year-week (ISO), year-month or year-quarter objects

#### Description 
Create or coerce using ``yearweek()``, ``yearmonth()``, or ``yearquarter()``

#### Usage
<pre><code>
yearweek(x)
is_53weeks(year)
yearmonth(x)
yearquarter(x)
</code></pre>

#### Arguments 
* x Other object. 
* year A vector of years.

#### Details 
It’s a known issue that these attributes will be dropped when using group_by and mutate together. 
It is recommended to ungroup ﬁrst, and then use mutate.

#### Value 
* Year-week (yearweek), year-month (yearmonth) or year-quarter (yearquarter) objects. 
* TRUE/FALSE if the year has 53 ISO weeks.

#### Index functions 
The tsibble ``yearmonth()`` and ``yearquarter()`` function preserve the time zone of the input x, contrasting to their zoo counterparts.

Examples
```{r}
# coerce POSIXct/Dates to yearweek, yearmonth, yearquarter ---
x <- seq(as.Date("2016-01-01"), as.Date("2016-12-31"), by = "1 month") 
yearweek(x) 
yearmonth(yearweek(x)); 
yearmonth(x)  
yearmonth("201807") 
yearquarter(x)
```
```{r}
# coerce numerics to yearmonth, yearquarter ---
yearmonth(seq(2010, 2017, by = 1 / 12)) 
yearquarter(seq(2010, 2017, by = 1 / 4))
```
```{r}
# coerce yearmonths to yearquarter ---
y <- yearmonth(x) 
yearquarter(y)
```
```{r}
# S3 method seq() ---
wk1 <- yearweek(as.Date("2017-11-01")) 
wk2 <- yearweek(as.Date("2018-04-29")) 
```
```{r}
seq(from = wk1, to = wk2, by = 2) # by two weeks 
mth <- yearmonth(as.Date("2017-11-01")) 
seq(mth, length.out = 5, by = 1) # by 1 month 
seq(yearquarter(mth), length.out = 5, by = 1) # by 1 quarter 
is_53weeks(2015:2016)
```
