---
title: "Tsibble"
author: "Kevin O'Brien"
date: "24 September 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tsibble)
```
## ``tile`` Tiling window calculation

#### Description Tiling window without overlapping observations:
* ``tile()`` always returns a list.
* ``tile_lgl()``, ``tile_int()``, ``tile_dbl()``, ``tile_chr()`` use the same arguments as tile(), but return vectors of the corresponding type. 
* ``tile_dfr()`` ``tile_dfc()`` return data frames using row-binding & column-binding.

#### Usage
<pre><code>
tile(.x, .f, ..., .size = 1, .bind = FALSE)
tile_dfr(.x, .f, ..., .size = 1, .bind = FALSE, .id = NULL)
tile_dfc(.x, .f, ..., .size = 1, .bind = FALSE)
</code></pre>

#### Arguments 
* .x An object to slide over. .f A function, formula, or atomic vector. If afunction, it is used as is. If a formula, e.g. ~ .x + 2, it is converted to a function. There are three ways to refer to the arguments: • For a single argument function, use . • For a two argument function, use .x and .y • For more arguments, use ..1, ..2, ..3 etc This syntax allows you to create very compact anonymous functions.
Ifcharactervector,numericvector,orlist,itisconvertedtoanextractorfunction. Character vectors index by name and numeric vectors index by position; use a list to index by position and name at different levels.
* Within a list, wrap stringsinget-attr()toextractnamedattributes. Ifacomponentisnotpresent, the value of .default will be returned.

... Additional arguments passed on to .f. .size An integer for window size. If positive, moving forward from left to right; if negative, moving backward (from right to left). .bind If .x is a list, should .x be combined before applying .f? If .x is a list of data frames, row binding is carried out. .id If not NULL a variable with this name will be created giving either the name or the index of the data frame.
SeeAlso • tile2, ptile • slide for sliding window with overlapping observations • stretch for expanding more observations

#### Examples
```{r}
x <- 1:5 
lst <- list(x = x, y = 6:10, z = 11:15) 
tile_dbl(x, mean, .size = 2) 
tile_lgl(x, ~ mean(.) > 2, .size = 2) 
tile(lst, ~ ., .size = 2)
```

## ``tile2``
Tiling window calculation over multiple inputs simultaneously

#### Description 
Tiling window without overlapping observations: 
* tile2() and ptile() always returns a list. 
* tile2_lgl(),tile2_int(),tile2_dbl(),tile2_chr()usethesameargumentsastile2(), but return vectors of the corresponding type. 
* tile2_dfr() tile2_dfc() return data frames using row-binding & column-binding.

#### Usage 
<pre><code>
tile2(.x, .y, .f, ..., .size = 1, .bind = FALSE)
tile2_dfr(.x, .y, .f, ..., .size = 1, .bind = FALSE, .id = NULL)
tile2_dfc(.x, .y, .f, ..., .size = 1, .bind = FALSE)
ptile(.l, .f, ..., .size = 1, .bind = FALSE)
ptile_dfr(.l, .f, ..., .size = 1, .bind = FALSE, .id = NULL)
ptile_dfc(.l, .f, ..., .size = 1, .bind = FALSE)
</code></pre>

#### Arguments 
* .x Objects to slide over simultaneously. 
* .y Objects to slide over simultaneously. .f A function, formula, or atomic vector. If afunction, it is used as is. If a formula, e.g. ~ .x + 2, it is converted to a function. There are three ways to refer to the arguments: • For a single argument function, use . • For a two argument function, use .x and .y • For more arguments, use ..1, ..2, ..3 etc This syntax allows you to create very compact anonymous functions. Ifcharactervector,numericvector,orlist,itisconvertedtoanextractorfunction. Character vectors index by name and numeric vectors index by position; use a list to index by position and name at different levels. Within a list, wrap stringsinget-attr()toextractnamedattributes. Ifacomponentisnotpresent, the value of .default will be returned. ... Additional arguments passed on to .f. .size An integer for window size. If positive, moving forward from left to right; if negative, moving backward (from right to left). .bind If .x is a list, should .x be combined before applying .f? If .x is a list of data frames, row binding is carried out. .id If not NULL a variable with this name will be created giving either the name or the index of the data frame. .l Alistoflists. Thelengthof .l determinesthenumberofargumentsthat .f will be called with. List names will be used if present.
SeeAlso • tile • slide2 for sliding window with overlapping observations 
• stretch2 for expanding more observations

#### Examples
```{r}
x <- 1:5; y <- 6:10; z <- 11:15 
lst <- list(x = x, y = y, z = z) 
df <- as.data.frame(lst) 
tile2(x, y, sum, .size = 2) 
tile2(lst, lst, ~ ., .size = 2) 
tile2(df, df, ~ ., .size = 2) 
ptile(lst, sum, .size = 1) 
ptile(list(lst, lst), ~ ., .size = 2)
```
