---
title: "Tsibble"
author: "Kevin O'Brien"
date: "24 September 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tsibble)
```
## difference 
Lagged differences

#### Description 
Lagged differences

#### Usage 
<pre><code>
difference(x, lag = 1, differences = 1, default = NA, order_by = NULL)
</code></pre>
#### Arguments 

x A numeric vector. lag An positive integer indicating which lag to use. differences An positive integer indicating the order of the difference. default Value used for non-existent rows, defaults to NA. order_by Override the default ordering to use another vector.

#### Value 
A numeric vector of the same length as x.

#### Examples
```{r}
# examples from base 
difference(1:10, 2) 
difference(1:10, 2, 2) 
x <- cumsum(cumsum(1:10)) 
difference(x, lag = 2) 
difference(x, differences = 2)
```
```{r}
# Use order_by if data not already ordered (example from dplyr) 
tsbl <- tsibble(year = 2000:2005, value = (0:5) ^ 2, index = year) 
scrambled <- tsbl %>% slice(sample(nrow(tsbl)))
wrong <- mutate(scrambled, diff = difference(value)) 
arrange(wrong, year)
right <- mutate(scrambled, diff = difference(value, order_by = year)) 
arrange(right, year)
```

## ``fill_na`` 
Turn implicit missing values into explicit missing values

#### Description 
Turn implicit missing values into explicit missing values

#### Usage

<pre><code>
fill_na(.data, ...)
</code></pre>

## S3 method for class 'tbl_ts' fill_na(.data, ..., .full = FALSE)

#### Arguments 
* .data A data frame. ... A set of name-value pairs. 
The values will replace existing explicit missing values by variable, otherwise NA. 
The replacement values must be of the same type as the original one.
* .full FALSE to insert NA for each key within its own period. 
 - TRUE to ﬁll NA over the entire time span of the data (a.k.a. fully balanced panel).


#### Examples
```{r}
harvest <- tsibble( year = c(2010, 2011, 2013, 2011, 2012, 2014), 
  fruit = rep(c("kiwi", "cherry"), each = 3), 
  kilo = sample(1:10, size = 6), key = id(fruit), index = year )

# leave NA as is ---fill_na(harvest, .full = TRUE)
```
```{r}
full_harvest <- fill_na(harvest, .full = FALSE) 
full_harvest
```
```{r}
# use fill() to fill `NA` by previous/next entry 
full_harvest %>% group_by(fruit) %>% tidyr::fill(kilo, .direction = "down")
# replace NA with a specific value ---harvest %>% fill_na(kilo = 0L)
# replace NA using a function by variable ---harvest %>% fill_na(kilo = sum(kilo))
# replace NA using a function for each group ---harvest %>% group_by(fruit) %>% fill_na(kilo = sum(kilo))
# replace NA ---pedestrian %>% group_by(Sensor) %>% fill_na(Count = as.integer(median(Count)))
```
