---
title: "Tsibble"
author: "Kevin O'Brien"
date: "24 September 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tsibble)
```
## difference 
Lagged differences

#### Description 
Lagged differences

#### Usage 
<pre><code>
difference(x, lag = 1, differences = 1, default = NA, order_by = NULL)
</code></pre>
#### Arguments 

x A numeric vector. lag An positive integer indicating which lag to use. differences An positive integer indicating the order of the difference. default Value used for non-existent rows, defaults to NA. order_by Override the default ordering to use another vector.

#### Value 
A numeric vector of the same length as x.

#### Examples
```{r}
# examples from base 
difference(1:10, 2) 
difference(1:10, 2, 2) 
x <- cumsum(cumsum(1:10)) 
difference(x, lag = 2) 
difference(x, differences = 2)
```
```{r}
# Use order_by if data not already ordered (example from dplyr) 
tsbl <- tsibble(year = 2000:2005, value = (0:5) ^ 2, index = year) 
scrambled <- tsbl %>% slice(sample(nrow(tsbl)))
wrong <- mutate(scrambled, diff = difference(value)) 
arrange(wrong, year)
right <- mutate(scrambled, diff = difference(value, order_by = year)) 
arrange(right, year)
```
