
#### Part D Data preparation.
To follow the dplyr vignette, flights data set in nycflights13 package were used as an example.

```{r}
library(dplyr)
library(nycflights13)
```
```{r}
set.seed(123)
data <- sample_n(flights, 3)
```
```{r}
glimpse(data)
Variables:
$ year      (int) 2013, 2013, 2013
$ month     (int) 12, 7, 3
$ day       (int) 15, 17, 2
$ dep_time  (int) 2124, 651, 1636
$ dep_delay (dbl) -4, -9, 1
$ arr_time  (int) 2322, 936, 1800
$ arr_delay (dbl) 1, -28, 0
$ carrier   (chr) "UA", "DL", "WN"
$ tailnum   (chr) "N801UA", "N194DN", "N475WN"
$ flight    (int) 289, 763, 1501
$ origin    (chr) "EWR", "JFK", "LGA"
$ dest      (chr) "DTW", "LAX", "MKE"
$ air_time  (dbl) 88, 306, 103
$ distance  (dbl) 488, 2475, 738
$ hour      (dbl) 21, 6, 16
$ minute    (dbl) 24, 51, 36
```


####Part A. Data preparation 

<!------------------------------------------------------------------>

First we load the two packages that we are going to use: *dplyr* and *nycflights13*. 
There will be a warning message that we can ignore.
```{r}
library(dplyr)
library(nycflights13)
```

We will use the ***flights*** data set on *nycflights13*. 
To find out the number of rows (cases) and columns (variables) we can use the `dim()` command. 
The `summary()` command will give us a summary of the data.


```{r}
dim(flights)

summary(flights)

glimpse(flights)
```
For ease of use, lets just work with 5 cases. 
We can use the `select_n()` command to select 5 cases from the data set.


```{r}
set.seed(123)

data <- sample_n(flights, 5)
```

#### Basic method of use `select()` 

<!------------------------------------------------------------------>

Here we can select a set of variables by name


This data set includes the 16 columns shown above.

###3. Basic method of use `select()`.
At first, the ways of using `select()` were shown.

```{r}
select(data, year)
  year
1 2013
2 2013
3 2013
```
This process shows the way to take the year column out of data. To pick multiple columns, you can write the following.
```{r}


select(data, year, month, day)
  year month day
1 2013    12  15
2 2013     7  17
3 2013     3   2

```
If columns were sequential in the dataset, you could write the following to pick sequential columns.
```{r}

select(data, year:day)
  year month day
1 2013    12  15
2 2013     7  17
3 2013     3   2

```
If you want to remove a specific column, add - in the head of the column name as follows.
```{r}
select(data, -year, -month, -day)
  dep_time dep_delay arr_time arr_delay carrier tailnum flight origin dest air_time distance hour minute
1     2124        -4     2322         1      UA  N801UA    289    EWR  DTW       88      488   21     24
2      651        -9      936       -28      DL  N194DN    763    JFK  LAX      306     2475    6     51
3     1636         1     1800         0      WN  N475WN   1501    LGA  MKE      103      738   16     36
```
To remove sequential columns, put sequential columns in brackets () connected with a colon.
```{r}
select(data, -(year:day))
  dep_time dep_delay arr_time arr_delay carrier tailnum flight origin dest air_time distance hour minute
1     2124        -4     2322         1      UA  N801UA    289    EWR  DTW       88      488   21     24
2      651        -9      936       -28      DL  N194DN    763    JFK  LAX      306     2475    6     51
3     1636         1     1800         0      WN  N475WN   1501    LGA  MKE      103      738   16     36
```
It is also possible to pick columns by choosing the column number.
```{r}
select(data, 1, 2, 3)
select(data, 1:3)
  year month day
1 2013    12  15
2 2013     7  17
3 2013     3   2
```

Next topics are slightly advanced.

It is possible to pick sequential columns temporarily and remove some of these.
```{r}
select(data, year:day, -month)
  year day
1 2013  15
2 2013  17
3 2013   2

```
It is also possible to remove sequential columns and keep a part of these.
```{r}
select(data, -(year:day), month)
  dep_time dep_delay arr_time arr_delay carrier tailnum flight origin dest air_time distance hour minute month
1     2124        -4     2322         1      UA  N801UA    289    EWR  DTW       88      488   21     24    12
2      651        -9      936       -28      DL  N194DN    763    JFK  LAX      306     2475    6     51     7
3     1636         1     1800         0      WN  N475WN   1501    LGA  MKE      103      738   16     36     3

```
Even using a column number can give the same result with the column name. (The results are omitted.)
```{r}
select(data, 1:3, -2)
select(data, -(1:3), 2)
```
#### 4. Utility functions of `select()`.
Utility functions existing in `select()`, `summarise_each()` and `mutate_each()` in dplyr as well as some functions in the tidyr package.


Seven functions existed in the utility functions of `select()`.

- `starts_with(match, ignore.case = TRUE)`
- `ends_with(match, ignore.case = TRUE)`
- `contains(match, ignore.case = TRUE)`
- `matches(match, ignore.case = TRUE)`
- `num_range(prefix, range, width = NULL)`
- `one_of(...)`
- `everything()`
 

We now check the respective commands and how to use them.

First, `starts_with()` picks columns whose name starts with the specified string.
```{r}
select(data, starts_with("arr"))
  arr_time arr_delay
1     2322         1
2      936       -28
3     1800         0
```
The argument `ignore.case` specifies whether the lowercase is classified as a capital letter(default is TRUE).

The `ends_with()` picks columns whose name ends with the specified string .
```{r}
select(data, ends_with("time"))
  dep_time arr_time air_time
1     2124     2322       88
2      651      936      306
3     1636     1800      103
```
The `contains()` picks columns whose name contains the specified string.
```{r}
select(data, contains("_"))
  dep_time dep_delay arr_time arr_delay air_time
1     2124        -4     2322         1       88
2      651        -9      936       -28      306
3     1636         1     1800         0      103
```
The `matches()` picks columns based on a regular expression matching string.
```{r}
select(data, contains("_"))
  dep_time dep_delay arr_time arr_delay air_time
1     2124        -4     2322         1       88
2      651        -9      936       -28      306
3     1636         1     1800         0      103
```
When the numbers were included in column names, `num_range()` might be useful. 
In this example, we change the column names to be x1–x16 and execute num_range() command for the data set.
```{r}
data2 <- data
colnames(data2) <- sprintf("x%d", 1:16)
select(data2, num_range("x", 8:11))
  x8     x9  x10 x11
1 UA N801UA  289 EWR
2 DL N194DN  763 JFK
3 WN N475WN 1501 LGA
```
By specifying as `num_range("x", 8:11)`, columns x8 to x11 can be identified. 
Numbers in the column name are not necessarily sequential.
```{r}
select(data2, num_range("x", c(9, 11)))
      x9 x11
1 N801UA EWR
2 N194DN JFK
3 N475WN LGA
```
When column names were padded, the column name was shown as x01. 
Here, the argument width in `num_range()` might be useful. 
We now try this process for a data that changes the column names as x01–x16.
```{r}
data3 <- data
colnames(data3) <- sprintf("x%02d", 1:16)
select(data3, num_range("x", 8:11, width=2))
  x08    x09  x10 x11
1  UA N801UA  289 EWR
2  DL N194DN  763 JFK
3  WN N475WN 1501 LGA
```
By specifying as width=2, the zero filled columns can be picked out.

When a column is named as a vector or character string, `one_of()` might be useful. 
An error occurs in the following case with select().
```{r}
col_vector <- c("year", "month", "day")
select(data, col_vector)
Error: All select() inputs must resolve to integer column positions.
The following do not:
*  col_vector
```
However, an intended process occurs in the case of `one_of()`.
```{r}
select(data, one_of(col_vector))
  year month day
1 2013    12  15
2 2013     7  17
3 2013     3   2
```
The `everything()` selects all columns. (Result was omitted.)

```{r}
select(data, everything())
```
If add - is in the head of a utility function name, we can pick out all except for the area specified in the utility function.
```{r}
select(data, -starts_with("arr"))
  year month day dep_time dep_delay carrier tailnum flight origin dest air_time distance hour minute
1 2013    12  15     2124        -4      UA  N801UA    289    EWR  DTW       88      488   21     24
2 2013     7  17      651        -9      DL  N194DN    763    JFK  LAX      306     2475    6     51
3 2013     3   2     1636         1      WN  N475WN   1501    LGA  MKE      103      738   16     36
```
#### 5. Standard evaluation.
Thus far, we explained the normal `select()` function; however, the normal `select()` function cannot handle character strings as arguments. 
This might become a problem when column names are given as a string vector for example. 
To solve this problem, the `select_()` function was equipped in dplyr. (Caution: An underscore was added in the function name.) 
The use of the `select_()` function is the same as the `select()` except specifying columns by string; however, attention is needed when specifying a column name by a vector.

```{r}
select_(data, "year", "month", "day")
  year month day
1 2013    12  15
2 2013     7  17
3 2013     3   2
```
When specifying column names by a vector, the vector should be given the .dot argument.
```{r}
col_vector <- c("year", "month", "day")
select_(data, .dots = col_vector)
  year month day
1 2013    12  15
2 2013     7  17
3 2013     3   2
```
All arguments that can use the select() function are also possible candidates for the `select_()` function.
```{r}
select_(data, 'year:day')
select_(data, 'year:day', '-month')
select_(data, '-(year:day)')
select_(data, 'starts_with("arr")')
select_(data, '-ends_with("time")')
```

Furthermore, also in this case, the argument vector should be given the .dot argument in the `select_()` function.
```{r}
select_(data, .dots = c('starts_with("arr")', '-ends_with("time")'))
```

#### 6. References.
Introduction to dplyr 
https://cran.rstudio.com/web/packages/dplyr/vignettes/introduction.html

Help page for select() function 
> help("select", package = "dplyr")

