---
title: "``tibbletime::collapse_by``"
output: html_document
---

```{r setup, include=FALSE}
library(tibbletime)
```

Collapse a ``tbl_time`` object by its index

#### Description
Collapse the index of a tbl_time object by time period. The index column is altered so that all dates that fall in a specified interval share a common date.

#### Usage
<pre><code>
collapse_by(.tbl_time, period = "yearly", start_date = NULL, side = "end",
clean = FALSE, ...)
</code></pre>

#### Arguments
* ``.tbl_time``: A tbl_time object.
* ``period``: A character specification used for time-based grouping. The general format to use is "frequency period" where frequency is a number like 1 or 2, and period is an interval like weekly or yearly. There must be a space between the two.
Note that you can pass the specification in a flexible way:
• 1 Year: '1 year' / '1 Y' / '1 yearly' / 'yearly'
This shorthand is available for year, quarter, month, day, hour, minute, second, millisecond and microsecond periodicities.
Additionally, you have the option of passing in a vector of dates to use as custom and more flexible boundaries.
* ``start_date``: Optional argument used to specify the start date for the first group. The default is to start at the closest period boundary below the minimum date in the supplied index.
* ``side``: Whether to return the date at the beginning or the end of the new period. By default, the "end" of the period. Use "start" to change to the start of the period.
* ``clean``: Whether or not to round the collapsed index up / down to the next period boundary. The decision to round up / down is controlled by the side argument.
* ``...``: Not currently used.

#### Details
collapse_by() is a simplification of a call to dplyr::mutate() to collapse an index column using ``collapse_index()``.
```{r}
#### Examples
# Basic functionality 
-------------------------------------------------------
# Facebook stock prices

data(FB)
FB <- as_tbl_time(FB, date)
# Collapse to weekly dates
collapse_by(FB, "weekly")
```

A common workflow is to group on the collapsed date column to perform a time based summary

```{r}

FB %>%
collapse_by("yearly") %>%
dplyr::group_by(date) %>%
dplyr::summarise_if(is.numeric, mean)
# Grouped functionality 
-----------------------------------------------------
data(FANG)
FANG <- FANG %>%
as_tbl_time(date) %>%
dplyr::group_by(symbol)
```

Collapse each group to monthly, calculate monthly standard deviation for each column
```{r}
``
FANG %>%
collapse_by("monthly") %>%
dplyr::group_by(date, add = TRUE) %>%
dplyr::summarise_all(sd)
```
