---
title: "``tibbletime::create_series``"
output: html_document
---

```{r setup, include=FALSE}
library(tibbletime)
```

 Create a tbl_time object with a sequence of regularly spaced dates

#### Description
``create_series()`` allows the user to quickly create a tbl_time object with a date column populated with a sequence of dates.

#### Usage
<pre><code>
create_series(time_formula, period = "daily", class = "POSIXct",
include_end = FALSE, tz = "UTC", as_vector = FALSE)
</code></pre>

#### Arguments

* ``time_formula``: A period to create the series over. This is specified as a formula. See the Details section of filter_time() for more information.
* period A character specification used for time-based grouping. The general format to use is "frequency period" where frequency is a number like 1 or 2, and period is an interval like weekly or yearly. There must be a space between the two. Note that you can pass the specification in a flexible way:
• 1 Year: '1 year' / '1 Y' / '1 yearly' / 'yearly'
This shorthand is available for year, quarter, month, day, hour, minute, second, millisecond and microsecond periodicities.
* Additionally, you have the option of passing in a vector of dates to use as custom and more flexible boundaries.
* ``class``: One of "Date", "POSIXct", "hms", "yearmon", "yearqtr". The default is "POSIXct".
* ``include_end``: Whether to always include the RHS of the time_formula even if it does not match the regularly spaced index.
* ``tz``: Time zone of the new series.
* ``as_vector``: Should the series be returned as a vector instead of a tibble?

#### Examples
```{r}
# Every day in 2013
create_series(~'2013', 'daily')
```

```{r}
# Every other day in 2013
create_series(~'2013', '2 d')
# Every quarter in 2013
create_series(~'2013', '1 q')
```

```{r}
# Daily series for 2013-2015
create_series('2013' ~ '2015', '1 d')
```

```{r}
# Minute series for 2 months
create_series('2012-01' ~ '2012-02', 'M')
# Second series for 2 minutes
create_series('2011-01-01 12:10:00' ~ '2011-01-01 12:12:00', 's')
```

```{r}
# Date class
create_series(~'2013', 'day', class = "Date")
```

```{r}
# yearmon class
create_series(~'2013', 'month', class = "yearmon")
# hms class. time_formula specified as HH:MM:SS here
create_series('00:00:00' ~ '12:00:00', 'second' , class = "hms")
```

```{r}
# Subsecond series
create_series('2013' ~ '2013-01-01 00:00:01', period = "10 millisec")
milli <- create_series('2013' ~ '2013-01-01 00:00:01', period = ".1 sec")
# Check that 'milli' is correct by running:
# options("digits.secs" = 4)
# options("digits" = 18)
# milli$date
# as.numeric(milli$date)
```
